### 2025-10-02 thesis/design/definitions.tex
Further improve the design section

The following sets are subsequently used to introduce the functions

\begin{enumerate}
    \item $\mathcal{Q}$ – The set of all possible natural language queries
    \item $\mathcal{S}$ – The set of all possible database schemas
    \item $\mathcal{E}$ – The set of all possible execution functions for SQL validation
    \item $\mathcal{V}$ – The set of all possible embedding spaces
    \item $\mathcal{D}$ – The set of all possible distance indices over historically observed databases
    \item $\mathcal{C}$ – The set of all possible candidate sets $\mathcal{C}'$
    \item $\mathcal{Q}_{\mathcal{S}}$ – The set of all valid queries over the database schema $S$.
\end{enumerate}

@@

$$
nq: \mathcal{Q} \times \mathcal{S} \times E \times \mathcal{V} \times \mathcal{D} \rightarrow \Omega_{\mathcal{S}}
$$

@@

where $q \in \mathcal{Q}$, $s \in \mathcal{S}$, $e \in \mathcal{E}$, $v \in \mathcal{V}$, $d \in \mathcal{D}$, and $\omega \in \Omega_{\mathcal{S}}$.

@@

where $q \in \mathcal{Q}$ is the input natural language query, $s \in \mathcal{S}$ is
the reduced schema subset, $c \in \mathcal{C}'$ is the set of selected examples,
and $\omega \in \Omega_{\mathcal{S}}$ is the generated SQL query.

>>>>

The following sets are subsequently used to introduce the functions $nq$, $\sigma$, $\phi$, $\pi$, $\rho$ and $\nu$.

\begin{enumerate}
    \item $\mathcal{Q}$ – The set of all possible natural language queries.
    \item $\mathcal{S}$ – The set of all possible database schemas.
    \item $\mathcal{E}$ – The set of all possible execution functions for SQL validation.
    \item $\mathcal{V}$ – The set of all possible embedding spaces.
    \item $\mathcal{D}$ – The set of all possible distance indices over historically observed databases.
    \item $\mathcal{C}$ – The set of all possible candidate sets $\mathcal{C}'$.
    \item $\mathcal{Q}_{\mathcal{S}}$ – The set of all valid queries over the database schema $S$.
\end{enumerate}

@@

We define the query function $nq$ is collapsing a natural language question $q$,
the database schema $s$ and a indices over historically observed examples and
databases $v$ and $d$ into one SQL query candidate $\omega$.

$$
nq: \mathcal{Q} \times \mathcal{S} \times \mathcal{E} \times \mathcal{V} \times \mathcal{D} \rightarrow \Omega_{\mathcal{S}}
$$

@@

where $q \in \mathcal{Q}$ is the input natural language query, $s \in \mathcal{S}$
is the database schema, $e \in \mathcal{E}$ is the execution function for validation,
$v \in \mathcal{V}$ is the embedding space, $d \in \mathcal{D}$ is the distance index,
and $\omega \in \Omega_{\mathcal{S}}$ is the generated SQL query. The function is comprised
out of the subsequently defined function and follows the algorithm described in Algorithm~\ref{algorithms:nq}.

@@

where $q \in \mathcal{Q}$ is the input natural language query, $s \in \mathcal{S}$ is
the database schema, $c \in \mathcal{C}'$ is the set of selected examples,
and $\omega \in \Omega_{\mathcal{S}}$ is the generated SQL query.
